---
title: "WUP_04"
author: "Ashley Cook"
date: "summer 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
thedata<-read.csv(file="GSScsv.csv")
```

```{r eval=FALSE}
thedata <- thedata %>%
mutate(across(where(is.character), as.factor))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Mention that you intend to use chatGPT to the greatest extent possible. Give credit to chatGPT when you use it to create code in your report. Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

First we found out what data we had, then we looked at the helper file to look at what code we need for the new assignment. Then we went back to write up 3, and took a code from there, changed the variable names and ran the code. Now we have a factor variable called DEGREE. 

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
ggplot(thedata, aes(x = DEGREE, y = WORDSUM)) +
geom_boxplot(fill = "skyblue", color = "darkblue", outlier.shape = NA) +
theme_minimal() +
labs(x = "DEGREE", y = "WORDSUM") +
theme(plot.title = element_text(hjust = 0.5)) +
ggtitle("Fancy Box Plot")
```
  
The graduate high school is the highest out of the 5 degrees. The LT High School would not overlap with Junior College or graduate with that showing that it is very likely to be different schooling criteria. The graduate school does not overlap with High school which shows that it is also different. Graduate high school seems to be the highest out of the 5 schools with LT High School being the lowest.
  

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(WORDSUM~DEGREE,data=thedata)
```
```
Out of all the degrees, High School holds the most people with 85 sitting, with Junior College holding the least. The Junior College has the highest in min having an 8, while High School having the lowest with 2. The highest mean is a 10 that has the Graduates in first and High School being the lowest with an 8. All these degrees have different scores, but each have their different strengths


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
```{r}
model1 <- aov(WORDSUM~DEGREE,data=thedata)
summary.aov(model1)
```

  
There is a significant difference between the schooling of all 5 degrees.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
